### 2016-01-26 Irregular-occ/Irregular-occ.tex
.

>>>>

\begin{figure*}
\begin{centering}
\subfigure[Offset from the JPL ephemeris]{\includegraphics[width=8.8cm]{figures/JPL-EME_Triton.eps} \label{Fig:offxtanomxjpl}}
\subfigure[\textcolor{red}{Offset from the numerical integration}]{\includegraphics[width=8.8cm]{figures/Zhang-EME.eps} \label{Fig:offxtanomxni}}
\caption{Offsets of the declination of Carme by true anomaly from the JPL ephemeris and \textcolor{red}{from the numerical integration of the positions obtained in \cite{GomesJunior2015}}.
\label{Fig:offxanom}}
\end{centering}
\end{figure*}
